Wetting of the tarsal adhesive fluid determines underwater adhesion in ladybug beetles

### 2021-09-16 source/jeb_tex/manuscript.tex
reviewer responses edited based on thomas and michael's comments
revised MS sent to JEB

\corres{(\email{endlein01@mpip-mainz.mpg.de})}

\date{Received 11 May 2021; revised 11 May 2021} %CHECK DATE

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights (range: 2 - 90 mg) to get the corresponding force (resolution = 5 \textmu N). A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element (P-629.1CD, \emph{Physik Instrumente, Germany}, resolution = 3 nm), fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step for smoothing. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to measure the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped maximize the hair contact
with the surface. Next, a short pause (1 s) minimized any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion were done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

@@

\begin{figure}
\includegraphics[width=3.5in]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (cream) substrates in air and underwater
conditions (n=5 per box). The small black markers show the underlying data points. The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright. Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model (see text and Table \ref{tab:Model-parameters}).}
\end{figure}

@@

The male ladybug beetles used in our experiments are known to possess mostly discoidal hairs on their distal pad. Contact images show that these hair tips are approximately circular (eccentricity $\sim$ 0.04), which could allow mechanical pinning of the secreted fluid around its perimeter. Based on this knowledge, we modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
adhesive fluid of volume $V_{f}$, mediating contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

@@

Our experiments demonstrate that the ladybug beetle can attach underwater
to a hydrophobic substrate even without a bubble trapped around its
tarsal hairs. A previous study\citep{RN87} proposed that an air bubble
is necessary for underwater attachment in terrestrial beetles. This is, however,
only true for hydrophilic substrates, where a trapped air bubble can facilitate
underwater adhesion due to the hairs making contact in a de-wetted
environment. For a hydrophobic substrate, the adhesion is similar
regardless of whether the contact occurs in air or underwater conditions,
with or without a trapped bubble. Our theoretical calculations further
show that the bubble by itself has a negligible capillary contribution
to the net underwater adhesion of the pad. Direct force measurement
of a single similarly sized bubble making contact with a hydrophobic
substrate shows a maximum adhesion less than 50 \textmu N, which
further validates that the bubble's contribution is insignificant
(see supplementary section S4).

@@

Ladybug beetles rely primarily on their oily fluid secretion at the tarsal hair tips to adhere
to surfaces in both air and underwater conditions. The beetles can
attach underwater on a hydrophobic substrate even without a trapped
air bubble within its hairy pad, although it loses this ability on
a hydrophilic substrate. This is explained theoretically by the different
contact angle and interfacial tension of the secreted fluid in air
and underwater conditions. Further, the bubble itself has a negligible
capillary contribution to the total force. The trapped bubble can
promote adhesion only on a hydrophilic substrate by providing an air
medium to the adhesive fluid bridges inside it. Oil wettability, thus,
primarily controls the insect's adhesion in any given condition. 
Our study highlights how a fluid-mediated strategy can help achieve strong adhesion even underwater. A
similar argument also explains previously reported underwater adhesion force measurements
in geckos \citep{RN15}, which suggests the possibility of capillary
contributions to gecko adhesion mediated by an oil-like phospholipid layer. Future studies should characterise
the fluid secretion's interfacial properties with a particular substrate
to better understand the fundamental nature of an animal's adhesion.

@@

\ack{We are grateful to Prof. Dr. Eduard Arzt and Dr. Ren\' {e} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for fruitful discussions.}

>>>>

\corres{(\email{endlein@gmail.com})}

\date{Received 11 May 2021; revised 16 September 2021} %CHECK DATE

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights (range: 2 - 90 mg) to get the corresponding force (resolution = 5 \textmu N). A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element, used for precise lateral movements (step size = 75 nm). Additionally, a separate Z-piezo element (P-629.1CD, \emph{Physik Instrumente, Germany}, resolution = 3 nm), fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step for smoothing. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to measure the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped maximize the hair contact
with the surface. Next, a short pause (1 s) minimized any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion were done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging was used to aid in orienting the pad
with the substrate before a test.

@@

\begin{figure}
\includegraphics[width=3.5in]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (cream) substrates in air and underwater
conditions (n=5 per box). The small black markers show the underlying data points. The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright. Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model (see text and Table \ref{tab:Model-parameters}). Two-way ANOVA test showed a significant effect of the \emph{contact mode} (p=0.001, F=9.596, degrees of freedom=2) and \emph{substrate} (p<0.001, F=36.231, degrees of freedom=1). Significant interaction between the above two categories was seen (p=0.001, F=10.551, degrees of freedom=2). Post-hoc t-test analysis and linear mixed-effect model results are reported in supplementary material (section S3). }
\end{figure}

@@

The male ladybug beetles used in our experiments are known to possess mostly discoidal hairs on their distal pad. Contact images show that these hair tips are approximately circular (eccentricity $\sim$ 0.04), which could allow mechanical pinning of the secreted fluid around its perimeter. Based on this knowledge, we modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
adhesive fluid of volume $V_{f}$, mediating contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference (``Cassie state").

@@

Our experiments demonstrate that the ladybug beetle can attach underwater
to a hydrophobic substrate even without a bubble trapped around its
tarsal hairs. A previous study\citep{RN87} proposed that an air bubble
is necessary for underwater attachment in terrestrial beetles. This is, however,
only true for hydrophilic substrates, where a trapped air bubble can facilitate
underwater adhesion due to the hairs making contact in a de-wetted
environment. For a hydrophobic substrate, the adhesion is similar
regardless of whether the contact occurs in air or underwater conditions,
with or without a trapped bubble. Our theoretical calculations further
show that the bubble by itself has a negligible capillary contribution (less than 3\%)
to the net underwater adhesion of the pad. Direct force measurement
of a single similarly sized bubble making contact with a hydrophobic
substrate shows a maximum adhesion less than 50 \textmu N, which
further validates that the bubble's contribution is insignificant
(see supplementary section S4).

@@

Ladybug beetles rely primarily on their oily fluid secretion at the tarsal hair tips to adhere
to surfaces in both air and underwater conditions. The beetles can
attach underwater on a hydrophobic substrate even without a trapped
air bubble within its hairy pad, although it loses this ability on
a hydrophilic substrate. This is explained theoretically by the different
contact angle and interfacial tension of the secreted fluid in air
and underwater conditions. Further, the bubble itself has a negligible
capillary contribution (less than 3\%) to the total force. The trapped bubble can
promote adhesion only on a hydrophilic substrate by providing an air
medium to the adhesive fluid bridges inside it. Oil wettability, thus,
primarily controls the insect's adhesion in any given condition. 
Our study highlights how a fluid-mediated strategy can help achieve strong adhesion even underwater. A
similar argument also explains previously reported underwater adhesion force measurements
in geckos \citep{RN15}, which suggests the possibility of capillary
contributions to gecko adhesion mediated by an oil-like phospholipid layer. Future studies should characterise
the fluid secretion's interfacial properties with a particular substrate
to better understand the fundamental nature of an animal's adhesion.

@@

\ack{We are grateful to Prof. Dr. Eduard Arzt and Dr. Ren\' {e} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for fruitful discussions. We further thank the referees for their valuable suggestions in improving the text.}
